### 2021-11-23 documentos/generators.tex
TODO: Tell someone to implement this

There exists a subset of PCE quantum channels that generate 
all PCE's, and the existence of these PCE generators may be explained with 
the vector space point of view.
%\janote{Este párrafo lo voy a retocar. El enunciado de arriba es el primer enunciado
%del nuevo párrafo. Ojo que hay que introducir la notación $\mcG$.}
By standard theorems of linear algebra, any subspace $W$ [see. \Eref{eq:19}] can be extended to a
maximal (non-trivial) subspace of dimension $2N-1$ by adjoining appropriate
additional basis elements. This can clearly be done in different ways. 
We therefore arrive to the set of maximal extensions of $W$,
where every maximal subspace corresponds to a PCE quantum channel that 
preserves $2^{2N-1}$ (half the) Pauli components $\paulicomponents$ 
of density matrix $\rho$. The
intersection of all the elements of this set reduces to $W$ itself, meaning 
that all PCE's can be obtained as intersections of maximal PCE's, the
PCE generators $\mcG$. Intersections of the maximal subspaces translates into 
compositions of the generators $\mcG$ to obtain any PCE.
Compositions of generators $\mcG$ can be understood intuitively from PCE diagrams
in \Fref{fig:examplesPCE}; the composition of any two 2-qubits PCE generators 
in (c), (d), or (e) is represented by taking the intersection between them both
and the three different possible compositions result in PCE channel in (b).
The existence of the PCE generators $\mcG$ provide the program of 
constructing all PCE channels a tool that avoids the usage of a 
high-computational-cost method. In a moment, we will discuss how to find the 
generators $\mcG$ from matrix $A$, given a symmetry that is obeyed both by the generators 
$\mcG$ and matrix $A$ in \Eref{eq:san}.
%For the case of 1 qubit, the existence of PCE generators $\pceg$ is  
%verified by Siudzińska~\cite{siudzinska2019geometry}.
%\janote{Esto puede
%ser un párrafo, o puede ser un comentario final dentro del párrafo antrerior.}

>>>>

There exists a subset of PCE channels that generate 
all PCEs; the nature of these generators may be studied, as we
shall see, with the properties of the aforementioned vector space.
%\janote{Este párrafo lo voy a retocar. El enunciado de arriba es el primer enunciado
%del nuevo párrafo. Ojo que hay que introducir la notación $\mcG$.}
By standard theorems of linear algebra, any subspace $W$, see \Eref{eq:19}, 
can be extended to a maximal non-trivial subspace of dimension $2N-1$ by
adjoining appropriate additional basis elements. This can be done in
different ways. We therefore arrive to the set of maximal extensions of $W$,
where every maximal subspace corresponds to a PCE quantum channel that
preserves half of the Pauli components. The intersection of all the elements of
this set reduces to $W$ itself,
and since intersection of subspaces translates to composition of PCEs,
this implies that all PCEs \cpnote{damm la identidad} can be obtained as
compositions the PCEs corresponding to maximally non-trivial subspaces, 
which we call generators. 
Compositions of generators can be understood intuitively from PCE
diagrams in \Fref{fig:examplesPCE}; the composition of any two 2-qubits PCE
generators 
in (c), (d), or (e) is represented by taking the intersection between them both
and the three different possible compositions result in PCE channel in (b).
The existence of the PCE generators $\mcG$ provide the program of 
constructing all PCE channels a tool that avoids the usage of a 
high-computational-cost method. In a moment, we will discuss how to find the 
generators $\mcG$ from matrix $A$, given a symmetry that is obeyed both by the generators 
$\mcG$ and matrix $A$ in \Eref{eq:san}.
%For the case of 1 qubit, the existence of PCE generators $\pceg$ is  
%verified by Siudzińska~\cite{siudzinska2019geometry}.
%\janote{Esto puede
%ser un párrafo, o puede ser un comentario final dentro del párrafo antrerior.}
